---
title: "p8105_hw6_fj2269"
author: "Fangming Jin"
date: "11/15/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
library(mgcv)
library(rnoaa)
```

**Question 1**

**Clean dataset**
```{r Q1S1, message=FALSE, warning=FALSE}
birthweight = read_csv(file = "./data/birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(babysex = factor(babysex, labels = c("male", "female")),
         frace = factor(frace, labels = c("White", "Black", " Asian", "Puerto Rican","Other")),
         malform = factor(malform, labels = c("absent", "present")),
         mrace = factor(mrace, labels = c("White", "Black", " Asian", "Puerto Rican")),
         ) %>%
  drop_na()
birthweight
```

**build the model**

I refer result of literature published in Journal of education and health promotion: Risk factors of low birth weight and effect of them on growth pattern of children up to sixth months of life: A cross-sectional study.

In this study, mother's age and weight, GA during delivery have a significant relationship with birth weight. So we use momage, delwt and gaweeks as predictors to build a linear regression model.
```{r Q1S2}
model = birthweight %>% 
  lm(bwt ~ momage + delwt + gaweeks, data = .) %>% 
  summary()
tidy_model = birthweight %>% 
  lm(bwt ~ momage + delwt + gaweeks, data = .) %>% 
  broom::tidy()
model
```
the parameter of predictor momage is 9.997, the parameter of predictor delwt is 5.44, the parameter of gaweeks is 60.76. the intercept is -275.69.

As we can see from this model, The p-value of these three predictors are much less than 0.05, which means that effect of mother weight, age and baby GA on baby birth weight is significant. The p-value of anova is < 2.2e-16, which means that the overall influence of covariate is significant. Adjusted R-squared is 0.2319. 23% of the variance found in the response variable (birth weight) can be explained by the predictor variable

The fitting formula of this model is as below:

estimated Y_{bwt}=-275.69+10I(Trt = age)+5.44I(Trt = weight)+60.76I(Trt = gaweeks)

**Residual vs fitted value**

```{r Q1S3}
lm_birthweight = lm(bwt ~ momage + delwt + gaweeks, data = birthweight)
plot = birthweight %>% 
  modelr::add_predictions(lm_birthweight) %>% 
  modelr::add_residuals(lm_birthweight) %>% 
  rename("prediction" = pred, "residual" = resid) %>%
  ggplot(aes(x = prediction, y = residual)) +
    geom_point(size = 1, alpha = 0.5, color = "brown") +
    labs(title = "Plot of Residual vs fitted value", x="Predicted/Fitted value", y="Residual") + 
    geom_abline(intercept = 0, slope = 0)
plot
```

**Compare of models**

We need to compare my model with another two model:

model A: using length at birth and gestational age as predictors (main effects only)

model B: using head circumference, length, sex, and all interactions (including the three-way interaction) between these

The result of model A is as below:

```{r}
lm(bwt ~ blength + gaweeks, data = birthweight) %>% summary()
```

The result of model B is as below:

```{r}
lm(bwt ~ bhead * blength * babysex, data = birthweight) %>% summary()
```

```{r Q2S3SS2}
cross_valid = 
  crossv_mc(birthweight, 100) %>%
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>%
  mutate(model1_mod  = map(train, ~lm(bwt ~ momage + delwt + gaweeks, data = .x)),
         model2_mod  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         model3_mod  = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x))) %>% 
  mutate(rmse_model1 = map2_dbl(model1_mod, test, ~rmse(model = .x, data = .y)),
         rmse_model2 = map2_dbl(model2_mod, test, ~rmse(model = .x, data = .y)),
         rmse_model3 = map2_dbl(model3_mod, test, ~rmse(model = .x, data = .y))) %>%
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model),
         model = recode(model, "model1" = "my model", "model2" = "model A", "model3" = "model B")) %>% 
  ggplot(aes(x = model, y = rmse)) + 
    geom_violin(aes(fill = model), color = "black", alpha = .5) +
    labs(title = "Comparision of three models", y="RMSE value") +
    theme(plot.title = element_text(hjust = 0.5), axis.title.x=element_blank())
cross_valid
```

As we can see from the violin plot, model B have the lowest mean and median of root mean squared errors, the model I built have the highest mean and median of root mean squared errors, and model A is in the middle. This means in these three model, prediction accuracy of model B is relatively high, the prediction accuracy of my model is relatively low, the prediction accuracy of model A is in the middle.

**Question 2**

First we use 5000 bootstrap samples and produce estimates of these two quantities for each bootstrap sample.
```{r Q2S1}
weather_df = 
  meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
bootstrap_weather = 
  weather_df %>%
  modelr::bootstrap(n = 5000) %>%
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance),
    results2 = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results, results2) %>% 
  select(.id, r.squared, term, estimate) %>%
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>%
  rename("intercept" = `(Intercept)`) %>%
  mutate(log = log(intercept*tmin, base = exp(1))) %>%
  select(r.squared, log)
bootstrap_weather
```

Plot the distribution of two quantity
```{r Q2S2SS1}
plot_boot1 = bootstrap_weather %>%
  ggplot(aes(x = r.squared)) +
    geom_density(fill = "orange", color = "black", alpha = 0.5) +
    labs(title = "Distribution of r squared", x="r squared", y="density") +
    theme(plot.title = element_text(hjust = 0.5))
plot_boot1
```

through cruve above is still skewed for its left tail is longer than the right one. The distribution of r squared is closed to normal distribution. Its mean is `r round(mean(pull(bootstrap_weather, r.squared)),4)`, its sd is `r round(sd(pull(bootstrap_weather, r.squared)),4)`

```{r Q2S2SS2}
plot_boot2 = bootstrap_weather %>%
  ggplot(aes(x = log)) +
    geom_density(fill = "blue", color = "black", alpha = 0.5) +
    labs(title = "Distribution of log(β0*β1)", x="log(β0*β1)", y="density") +
    theme(plot.title = element_text(hjust = 0.5))
plot_boot2
```

Through the distribution of value on the peak of this cruve is a little bit irregular.The distribution of log of estimated beta0 multiple beta1 is closed to normal distribution. Its mean is `r round(mean(pull(bootstrap_weather, log)),4)`, its sd is `r round(sd(pull(bootstrap_weather, log)),4)`

95% CI for r squared and log(beta0*beta1)
```{r Q2S3}
lower_limit_r = quantile(pull(bootstrap_weather,r.squared), probs = c(0.025, 0.975)) %>% 
  .[[1]] %>%
  round(., 3)
upper_limit_r = quantile(pull(bootstrap_weather,r.squared), probs = c(0.025, 0.975)) %>% 
  .[[2]] %>%
  round(., 3)
lower_limit_log = quantile(pull(bootstrap_weather,log), probs = c(0.025, 0.975)) %>% 
  .[[1]] %>%
  round(., 3)
upper_limit_log = quantile(pull(bootstrap_weather,log), probs = c(0.025, 0.975)) %>% 
  .[[2]] %>%
  round(., 3)
```
The 95% CI for r squared is (`r lower_limit_r`, `r upper_limit_r`), The 95% CI for log(beta0*beta1) is (`r lower_limit_log`, `r upper_limit_log`)